### 2022-01-12 input/experiments.tex
move complexity to expe + positioning fig + small fix

>>>>

\TODO{Each \process has a space complexity of $\mathcal{O}(\log_2(d \cdot
|V|))$, and generates messages of identical space complexity. In terms
of number messages, in the average case, a \process $x$ chosen
uniformly at random among all \processes creates a logical
partition. Its messages $\alpha_x$ spread through the network until
reaching \processes that belong to another partition closer to
them. This splits partitions in half on average. Overall, the $n^{th}$
new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
      \log_2 n \rfloor}})$} \processes. This decreases every new
partition until reaching one \process per new partition: its
source. The average number of messages per \process is
\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
number of neighbors per \process.}
\TODO{\TODO{Multiple receipt and multiple delivery} In terms of number of
messages, deleting the $a^{th}$ partition generates twice as many
messages as creating the $a^{th}$ partition: $\delta$ messages travel
through the partition, then $\alpha$ messages compete to fill the gap
\TODO{which is?}. \TODO{What about false positives?} Overall, the
communication complexity shows that \NAME scales well to the number of
partitions.}

%% In the
%% worst-case, every new partition includes all but one \process
%% belonging to the previous partition. The total number of messages
%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
%% a^2)$. As for the average-case, the number of messages for the
%% partition deletion is identical to the number of messages of the
%% corresponding partition creation.

### 2022-01-12 input/proposal.tex
move complexity to expe + positioning fig + small fix

Each \process has a space complexity of $\mathcal{O}(\log_2(d \cdot
|V|))$, and generates messages of identical space complexity. In terms
of number messages, in the average case, a \process $x$ chosen
uniformly at random among all \processes creates a logical
partition. Its messages $\alpha_x$ spread through the network until
reaching \processes that belong to another partition closer to
them. This splits partitions in half on average. Overall, the $n^{th}$
new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
      \log_2 n \rfloor}})$} \processes. This decreases every new
partition until reaching one \process per new partition: its
source. The average number of messages per \process is
\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 n
      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
number of neighbors per \process.

While adding logical partitions to the distributed system is
straightforward and lightweight, removing them introduces additional
complexity and costs caused by concurrent operations.

@@

Delete operations bring a new notion of order between events, and most
importantly between message deliveries. A \process $s$ that performs a
\texttt{Del} operation implicitly states that all its preceding
\texttt{Add} operations become obsolete. As consequence, their results
-- scoped broadcast in the form of \texttt{\underline{A}dd}
notifications $\alpha_s$ -- should be canceled by the corresponding
\texttt{\underline{D}el} notifications of staleness $\delta_s$. We
focus on the last delivery of each \process, since the best is also
the last, as highlighted by Algorithm~\ref{algo:add}. \TODO{More about
  useless $\alpha$ ?}

@@

\TODO{Multiple receipt and multiple delivery} In terms of number of
messages, deleting the $a^{th}$ partition generates twice as many
messages as creating the $a^{th}$ partition: $\delta$ messages travel
through the partition, then $\alpha$ messages compete to fill the gap
\TODO{which is?}. \TODO{What about false positives?} Overall, the
communication complexity shows that \NAME scales well to the number of
partitions.
%% In the
%% worst-case, every new partition includes all but one \process
%% belonging to the previous partition. The total number of messages
%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
%% a^2)$. As for the average-case, the number of messages for the
%% partition deletion is identical to the number of messages of the
%% corresponding partition creation.

@@

\TODO{Transition to experiments.}

>>>>

Adding logical partitions to a static network is straightforward and
lightweight. Unfortunately, removing partitions or introducing dynamic
network membership increases complexity and costs caused by concurrent
operations.

@@

Delete operations bring a new notion of order between events, and most
importantly between message deliveries. A \process $s$ that performs a
\texttt{Del} operation implicitly states that its preceding
\texttt{Add} operation becomes obsolete. As consequence, their results
-- scoped broadcast in the form of \texttt{\underline{A}dd}
notifications $\alpha_s$ -- should be canceled by the corresponding
\texttt{\underline{D}el} notifications of staleness $\delta_s$. We
focus on the last delivery of each \process, since the best is also
the last, as highlighted by Algorithm~\ref{algo:add}.

%% \TODO{More about useless $\alpha$ ?}

@@

@@

\NAME follows the principles of scoped broadcast to efficiently and
consistently propagate notifications to \processes that need them
despite concurrent operations. \TODO{Next section aims at providing
empirical evidence of the scalability and properties of \NAME.}
